\textbf{Sharp Bias-variance Tradeoffs of Hard Parameter Sharing in High-dimensional Linear Regression}

### 2020-10-20 arxiv_full_version/proof_examples.tex
appendix

	=& ((x-1)^2\kappa^2 + (x^2+1)d^2){p^{-1}} \tr\left[ (X^{(1)})^\top X^{(1)} \hat \Sigma(x)^{-1}(X^{(2)})^\top X^{(2)}\right]+\sigma^2(n_1+n_2-p), \label{EgA}

@@

For the first step, it is easy to observe that $h(x)< h(-x)$ for any positive $x$.
Hence the minimum of $h(x)$ is achieved when $x$ is positive.
%$h(1)=\OO(pd^2 + \sigma^2)$ and $ h(w)\gtrsim p\kappa^2 \gg h(1)$ for $w\ge 2$ or $w\le 1/2$.  Hence it suffices to consider the case $1/2\le w\le 2$.
Next, we consider the case where $x\ge 1$.
Notice that the following function always increases when $x$ increases in the positive orthant:
$$\tr\left[\left([(X^{(2)})^\top X^{(2)}]^{-1} + x^{-2} [(X^{(1)})^\top X^{(1)}]^{-1}\right)^{-1}\right]$$
By taking the derivative of $h(x)$, we obtain that for any $x > 1+d^2/\kappa^2$,
\begin{align}\label{h'(A)1}
h'(x) \ge \left[2(1-x^{-1})\frac{\kappa^2}{x^2} - 2\frac{d^2}{x^3}\right] \cdot p^{-1} \tr\left[\left([(X^{(2)})^\top X^{(2)}]^{-1} + x^{-2} [(X^{(1)})^\top X^{(1)}]^{-1}\right)^{-1}\right] > 0,
\end{align}
Finally, we consider the case where $x \le 1$. Notice that the following function always decreases when $x$ decreases from $1$:
$$\tr\left[\left(x^2[(X^{(2)})^\top X^{(2)}]^{-1} +  [(X^{(1)})^\top X^{(1)}]^{-1}\right)^{-1}\right].$$
Hence, by taking derivative of $h(x)$, we obtain that for any $x\le 1-d^2/\kappa^2$,
\begin{align}\label{h'(A)2}
	h'(x)\le [-2(1-x)\kappa^2 +2 xd^2] \cdot p^{-1} \tr\left[\left(x^2[(X^{(2)})^\top X^{(2)}]^{-1} + [(X^{(1)})^\top X^{(1)}]^{-1}\right)^{-1}\right] < 0,
\end{align}
In summary, the global minimizer of $h(x)$ lies within $1-d^2/\kappa^2$ and $1+d^2/\kappa^2$.

@@

Second, we prove equation \eqref{claim_largedev2}.
The proof is very similar to Claim \ref{claim_largedev1}.
The key difference is that $\hat x$ correlates with $\epsilon^{(1)}$, $\epsilon^{(2)}$, $\beta^{(1)}$, and $\beta^{(2)}$.
Nevertheless, Lemma \ref{largedeviation} still applies for any arbitrary $\hat x$.
We describe a proof sketch and omit the details.
Recall that $\beta_0$ is the shared component of $\beta^{(1)}$ and $\beta^{(2)}$ with i.i.d. Gaussian entries of mean zero and variance $p^{-1}\kappa^2$.
The task-specific components, denoted by $\wt\beta^{(1)}$ and $\wt\beta^{(2)}$, consist of i.i.d. Gaussian random variables with mean zero and variance $p^{-1} d^2$.
We write $L(\hat{\beta}_2^{\MTL}) $ from equation \eqref{Lbeta_HPS} as:
\begin{align}
L(\hat{\beta}_2^{\MTL})  =&  \left\| (\Sigma^{(2)})^{1/2}\hat \Sigma(\hat x)^{-1} \left[(X^{(1)})^\top X^{(1)} (\hat x -\hat x^2)\beta_0+(X^{(1)})^\top X^{(1)} \hat x\wt \beta^{(1)} - (X^{(1)})^\top X^{(1)}  \hat x^2\wt \beta^{(2)} \right] \right. \nonumber\\
&\left. + (\Sigma^{(2)})^{1/2}\hat \Sigma(\hat x)^{-1}\left[ (X^{(2)})^\top \epsilon^{(2)} + \hat x   (X^{(1)})^\top \epsilon^{(1)} \right]\right\|^2. \label{expand_15}
\end{align}
Similar to the analysis of $g(x)$, we expand $L(\hat{\beta}_2^{\MTL})$ into the sum of 15 terms, and bound the concentration error of each term similar to $h_1(x), \dots, h_6(x)$.
For example, for the leading term $\hat x^2 (\wt \beta^{(1)})^\top (X^{(1)})^\top X^{(1)} \hat \Sigma(\hat x)^{-1}  \Sigma^{(2)} \hat \Sigma(\hat x)^{-1}  (X^{(1)})^\top X^{(1)}\wt\beta^{(1)}$, using
Lemma \ref{largedeviation} and the operator norm bounds, we obtain the following estimate w.h.p.
\begin{align*}
&  \left| (\wt \beta^{(1)})^\top (X^{(1)})^\top X^{(1)} \hat \Sigma(\hat x)^{-1}  \Sigma^{(2)} \hat \Sigma(\hat x)^{-1}  (X^{(1)})^\top X^{(1)}\wt\beta^{(1)} - \frac{d^2}{p}\bigtr{(X^{(1)})^\top X^{(1)} \hat \Sigma(\hat x)^{-1}  \Sigma^{(2)} \hat \Sigma(\hat x)^{-1}  (X^{(1)})^\top X^{(1)}}\right| \\
&\le p^{-1+c}d^2 \cdot \left\| (X^{(1)})^\top X^{(1)} \hat \Sigma(\hat x)^{-1}  \Sigma^{(2)} \hat \Sigma(\hat x)^{-1}  (X^{(1)})^\top X^{(1)} \right\|_F \\
&\le p^{-1/2+c}d^2 \cdot  \left\| (X^{(1)})^\top X^{(1)} \hat \Sigma(\hat x)^{-1}  \Sigma^{(2)} \hat \Sigma(\hat x)^{-1}  (X^{(1)})^\top X^{(1)} \right\|  \lesssim p^{-1/2+c}d^2.
\end{align*} 
For the cross term $\hat x (\wt \beta^{(1)})^\top (X^{(1)})^\top X^{(1)} \hat \Sigma(\hat x)^{-1}  \Sigma^{(2)} \hat \Sigma(\hat x)^{-1}  (X^{(2)})^\top  \epsilon^{(2)}$, using Lemma \ref{largedeviation} and the operator norm bounds, we obtain the following estimate w.h.p.
\begin{align*}
 \left| (\wt \beta^{(1)})^\top (X^{(1)})^\top X^{(1)} \hat \Sigma(\hat x)^{-1}  \Sigma^{(2)} \hat \Sigma(\hat x)^{-1}  (X^{(2)})^\top  \epsilon^{(2)}\right|  & \le p^c \cdot \sigma\sqrt{p^{-1}d^2} \cdot \|(X^{(1)})^\top X^{(1)} \hat \Sigma(\hat x)^{-1}  \Sigma^{(2)} \hat \Sigma(\hat x)^{-1}  (X^{(2)})^\top  \|_F \\
&\lesssim p^{c}\cdot \sigma d \cdot  \|(X^{(1)})^\top X^{(1)} \hat \Sigma(\hat x)^{-1}  \Sigma^{(2)} \hat \Sigma(\hat x)^{-1}  (X^{(2)})^\top  \| \\
&\lesssim p^{-1/2+c}\sigma d\le p^{-1/2+c}(\sigma^2+ d^2).
\end{align*}
The rest of the terms in the expansion of $L(\hat{\beta}_2^{\MTL})$ can be dealt with similarly, and we omit the details.
 \end{proof}

@@

For the bias term, since the spectrum of $(X^{(1)})^{\top} X^{(1)}$ is tightly concentrated by Fact \ref{fact_minv}, we have that
\begin{align}
 \frac{(\sqrt{n_1}-\sqrt{p})^4 \cdot (1- p^{-c_\varphi})}{p} \bigtr{\hat \Sigma^{-2}}  &\le {p}^{-1}\tr\left[\hat\Sigma^{-2} \left((X^{(1)})^\top X^{(1)} \right)^2\right] \label{eq_bias111}\\
 &\le \frac{(\sqrt{n_1}+\sqrt{p})^4 \cdot (1+ p^{-c_\varphi})}{p} \bigtr{\hat\Sigma^{-2}}.\nonumber
\end{align}
%To obtain this inequality, we used
%$$ (\sqrt{n_1}-\sqrt{p})^4 \cdot (1-p^{-c_\varphi}) \preceq \left((X^{(1)})^\top X^{(1)} \right)^2 \preceq (\sqrt{n_1}+\sqrt{p})^4 \cdot (1+ p^{-c_\varphi}) \quad \text{with high probability},$$
%by Fact \ref{fact_minv} (ii), and the fact that for the product of two PSD matrices, its trace is always nonnegative.
Using the bias limit \eqref{lem_cov_derv_eq} with $\Sigma^{(1)}=\Sigma^{(2)}=\Lambda=V=\id_{p\times p}$, and $w = e_i$ (the $i$-th coordinate vector), we have w.h.p. (via a union bound)
\begin{align*}%\label{eq_bias112}
 e_i^{\top}\hat\Sigma^{-2} e_i = \frac{1}{(n_1+n_2)^2} \left[\frac{a_3+a_4+1}{(a_1+a_2)^2} +\OO(p^{-c_\varphi})\right], \text{ for all } i = 1, 2, \dots, p.
\end{align*}
We solve the self-consistent equations \eqref{eq_a34extra} given $a_1, a_2$, and obtain
\begin{align*}
		a_3 = \frac{p\cdot n_1}{(n_1 +n_2)(n_1 +n_2 - p)}, \quad
		&  a_4 = \frac{p\cdot n_2}{(n_1 + n_2)(n_1 + n_2 - p)}. %\label{simplesovlea34}
\end{align*}
Applying $a_3, a_4$ to the equation above, we obtain
\begin{align*}%\label{eq_bias113}
 e_i^{\top}\hat\Sigma^{-2}e_i =  \frac{1}{(n_1+n_2)^2} \left[  \frac{ (n_1+n_2)^3 }{(n_1+n_2-p)^3} +\OO(p^{-c_\varphi})\right], \text{ for all } i = 1, 2, \dots, p.
\end{align*}
%In fact, we need this estimate to hold simultaneously for all $1\le i \le p$ with high probability. For this purpose, we shall use equation \eqref{apply derivlocal} to get that
%\begin{align*}%\label{eq_bias113}
%\left| \left(\hat\Sigma^{-2}\right)_{ii} - \frac{1}{(n_1+n_2)^2}\cdot \frac{(n_1+n_2)^3}{(n_1+n_2-p)^3}\right|\prec \frac{p^{-\frac{\varphi-4}{2\varphi}}}{(n_1+n_2)^2}
%\end{align*}
%on a high probability event that does not depend on $i$. Then using Fact \ref{lem_stodomin} (i), we obtain that
%\begin{align*}
%\left| \sum_{i=1}^p \left(\hat\Sigma^{-2}\right)_{ii} - \frac{p}{(n_1+n_2)^2}\cdot  \frac{(n_1+n_2)^3}{(n_1+n_2-p)^3}\right|\prec \frac{p^{1-\frac{\varphi-4}{2\varphi}}}{(n_1+n_2)^2}
%\end{align*}
%with high probability, which by Definition \ref{stoch_domination} gives that
%\begin{align}\label{eq_bias113}
%\left| p^{-1}\sum_{i=1}^p \left(\hat\Sigma^{-2}\right)_{ii} - \frac{1}{(n_1+n_2)^2}\cdot  \frac{(n_1+n_2)^3}{(n_1+n_2-p)^3}\right|\le \frac{p^{-c_\varphi}}{(n_1+n_2)^2}
%\end{align}
%with high probability.
Applying the above result to equation \eqref{eq_bias111}, we get the desired result for the bias term.
%\begin{align*}
%		& \frac{(\sqrt{n_1}-\sqrt{p})^4 \cdot (1- p^{-c_\varphi}) - n_1^2 \cdot (1+\OO(p^{-c_\varphi}))}{(n_1+n_2)^2}\cdot   \frac{(n_1+n_2)^3}{(n_1+n_2-p)^3}\nonumber \\
%		\le &  {p}^{-1}\tr\left[\hat\Sigma^{-2} \left((X^{(1)})^\top X^{(1)} \right)^2\right] - \frac{n_1^2}{(n_1+n_2)^2}\cdot  \frac{(n_1+n_2)^3}{(n_1+n_2-p)^3} \nonumber\\
%		\le &  \frac{(\sqrt{n_1}+\sqrt{p})^4 \cdot (1+ p^{-c_\varphi}) - n_1^2 \cdot (1+\OO(p^{-c_\varphi}))}{(n_1+n_2)^2}\cdot   \frac{(n_1+n_2)^3}{(n_1+n_2-p)^3}.
%\end{align*}
Combining the bias and variance estimates, we get that
\begin{align*}
	\left|L(\hat{\beta}_2^{\MTL})  -  \frac{2d^2 n_1^2 (n_1+n_2)}{(n_1 + n_2 - p)^3} - \frac{\sigma^2 p}{n_1+n_2-p}   \right| &\le   \left[\left( 1+\sqrt{\frac{p}{n_1}}\right)^4-1\right] \cdot \frac{2d^2n_1^2 (n_1+n_2)}{(n_1 + n_2 - p)^3} \\
	&+\OO\left( p^{-c_\varphi} (\sigma^2 + d^2)+ \frac{d^4 + \sigma^2 d^2}{\kappa^2}+p^{-1/2+2c}\kappa^2 +  p^{-1/4+c} (\sigma^2 +d^2) \right).
\end{align*}
Since $\sigma^2 \lesssim  \kappa^2$ and $d^2 \le p^{-\e}{\kappa^2}$ by our assumption, we obtain the desired result.
The proof is complete.
\end{proof}

>>>>

	=& [(x-1)^2\kappa^2 + (x^2+1)d^2]\cdot {p^{-1}} \tr\left[ (X^{(1)})^\top X^{(1)} \hat \Sigma(x)^{-1}(X^{(2)})^\top X^{(2)}\right]+\sigma^2(n_1+n_2-p), \label{EgA}

@@

For the first step, it is easy to observe that $h(x)< h(-x)$ for any positive $x$.
Hence the minimum of $h(x)$ is achieved when $x$ is positive.
%$h(1)=\OO(pd^2 + \sigma^2)$ and $ h(w)\gtrsim p\kappa^2 \gg h(1)$ for $w\ge 2$ or $w\le 1/2$.  Hence it suffices to consider the case $1/2\le w\le 2$.
Next, we consider the case where $x\ge 1$.
Notice that the following function always increases when $x$ increases in the positive orthant:
$$\tr\left[\left([(X^{(2)})^\top X^{(2)}]^{-1} + x^{-2} [(X^{(1)})^\top X^{(1)}]^{-1}\right)^{-1}\right]$$
By taking the derivative of $h(x)$, we obtain that for any $x > 1+d^2/\kappa^2$,
\begin{align}\label{h'(A)1}
h'(x) \ge \left[2(1-x^{-1})\frac{\kappa^2}{x^2} - 2\frac{d^2}{x^3}\right] \cdot p^{-1} \tr\left[\left([(X^{(2)})^\top X^{(2)}]^{-1} + x^{-2} [(X^{(1)})^\top X^{(1)}]^{-1}\right)^{-1}\right] > 0,
\end{align}
Finally, we consider the case where $x \le 1$. Notice that the following function always decreases when $x$ decreases from $1$:
$$\tr\left[\left(x^2[(X^{(2)})^\top X^{(2)}]^{-1} +  [(X^{(1)})^\top X^{(1)}]^{-1}\right)^{-1}\right].$$
Hence, by taking derivative of $h(x)$, we obtain that for any $x\le 1-d^2/\kappa^2$,
\begin{align}\label{h'(A)2}
	h'(x)\le [-2(1-x)\kappa^2 +2 xd^2] \cdot p^{-1} \tr\left[\left(x^2[(X^{(2)})^\top X^{(2)}]^{-1} + [(X^{(1)})^\top X^{(1)}]^{-1}\right)^{-1}\right] < 0.
\end{align}
In summary, the global minimizer of $h(x)$ lies within $1-d^2/\kappa^2$ and $1+d^2/\kappa^2$.

@@

Second, we prove equation \eqref{claim_largedev2}.
The proof is very similar to Claim \ref{claim_largedev1}.
The key difference is that $\hat x$ correlates with $\epsilon^{(1)}$, $\epsilon^{(2)}$, $\beta^{(1)}$, and $\beta^{(2)}$.
Nevertheless, Lemma \ref{largedeviation} still applies for any arbitrary $\hat x$.
We describe a proof sketch and omit the details.
Recall that $\beta_0$ is the shared component of $\beta^{(1)}$ and $\beta^{(2)}$ with i.i.d. Gaussian entries of mean zero and variance $p^{-1}\kappa^2$.
The task-specific components, denoted by $\wt\beta^{(1)}$ and $\wt\beta^{(2)}$, consist of i.i.d. Gaussian random variables with mean zero and variance $p^{-1} d^2$.
We write $L(\hat{\beta}_2^{\MTL}) $ from equation \eqref{Lbeta_HPS} as:
\begin{align}
L(\hat{\beta}_2^{\MTL})  =&  \left\| (\Sigma^{(2)})^{1/2}\hat \Sigma(\hat x)^{-1} \left[(X^{(1)})^\top X^{(1)} (\hat x -\hat x^2)\beta_0+(X^{(1)})^\top X^{(1)} \hat x\wt \beta^{(1)} - (X^{(1)})^\top X^{(1)}  \hat x^2\wt \beta^{(2)} \right] \right. \nonumber\\
&\left. + (\Sigma^{(2)})^{1/2}\hat \Sigma(\hat x)^{-1}\left[ (X^{(2)})^\top \epsilon^{(2)} + \hat x   (X^{(1)})^\top \epsilon^{(1)} \right]\right\|^2. \label{expand_15}
\end{align}
Similar to the analysis of $g(x)$, we expand $L(\hat{\beta}_2^{\MTL})$ into the sum of 15 terms, and bound the concentration error of each term similar to $h_1(x), \dots, h_6(x)$.
For example, for the leading term 
\[\hat x^2 (\wt \beta^{(1)})^\top (X^{(1)})^\top X^{(1)} \hat \Sigma(\hat x)^{-1}  \Sigma^{(2)} \hat \Sigma(\hat x)^{-1}  (X^{(1)})^\top X^{(1)}\wt\beta^{(1)},\] 
using Lemma \ref{largedeviation} and the operator norm bounds, we obtain the following estimate w.h.p.
\begin{align*}
&  \left| (\wt \beta^{(1)})^\top (X^{(1)})^\top X^{(1)} \hat \Sigma(\hat x)^{-1}  \Sigma^{(2)} \hat \Sigma(\hat x)^{-1}  (X^{(1)})^\top X^{(1)}\wt\beta^{(1)} - \frac{d^2}{p}\bigtr{(X^{(1)})^\top X^{(1)} \hat \Sigma(\hat x)^{-1}  \Sigma^{(2)} \hat \Sigma(\hat x)^{-1}  (X^{(1)})^\top X^{(1)}}\right| \\
&\le p^{-1+c}d^2 \cdot \left\| (X^{(1)})^\top X^{(1)} \hat \Sigma(\hat x)^{-1}  \Sigma^{(2)} \hat \Sigma(\hat x)^{-1}  (X^{(1)})^\top X^{(1)} \right\|_F \\
&\le p^{-1/2+c}d^2 \cdot  \left\| (X^{(1)})^\top X^{(1)} \hat \Sigma(\hat x)^{-1}  \Sigma^{(2)} \hat \Sigma(\hat x)^{-1}  (X^{(1)})^\top X^{(1)} \right\|  \lesssim p^{-1/2+c}d^2.
\end{align*} 
For the cross term $\hat x (\wt \beta^{(1)})^\top (X^{(1)})^\top X^{(1)} \hat \Sigma(\hat x)^{-1}  \Sigma^{(2)} \hat \Sigma(\hat x)^{-1}  (X^{(2)})^\top  \epsilon^{(2)}$, using Lemma \ref{largedeviation} and the operator norm bounds, we obtain the following estimate w.h.p.
\begin{align*}
& \left| (\wt \beta^{(1)})^\top (X^{(1)})^\top X^{(1)} \hat \Sigma(\hat x)^{-1}  \Sigma^{(2)} \hat \Sigma(\hat x)^{-1}  (X^{(2)})^\top  \epsilon^{(2)}\right|  \\
  \le & p^c \cdot \sigma\sqrt{p^{-1}d^2} \cdot \|(X^{(1)})^\top X^{(1)} \hat \Sigma(\hat x)^{-1}  \Sigma^{(2)} \hat \Sigma(\hat x)^{-1}  (X^{(2)})^\top  \|_F \\
 \lesssim & p^{c}\cdot \sigma d \cdot  \|(X^{(1)})^\top X^{(1)} \hat \Sigma(\hat x)^{-1}  \Sigma^{(2)} \hat \Sigma(\hat x)^{-1}  (X^{(2)})^\top  \| \\
 \lesssim & p^{-1/2+c}\sigma d\le p^{-1/2+c}(\sigma^2+ d^2).
\end{align*}
The rest of the terms in the expansion of $L(\hat{\beta}_2^{\MTL})$ can be dealt with similarly, and we omit the details.
 \end{proof}

@@

For the bias term, since the spectrum of $(X^{(1)})^{\top} X^{(1)}$ is tightly concentrated by Fact \ref{fact_minv}, we have that
 \frac{(\sqrt{n_1}-\sqrt{p})^4 \cdot (1- p^{-c_\varphi})}{p} \bigtr{\hat \Sigma^{-2}}  &\le {p}^{-1}\tr\left[\hat\Sigma^{-2} \left((X^{(1)})^\top X^{(1)} \right)^2\right] \label{eq_bias111}\\
 &\le \frac{(\sqrt{n_1}+\sqrt{p})^4 \cdot (1+ p^{-c_\varphi})}{p} \bigtr{\hat\Sigma^{-2}}.\nonumber
%To obtain this inequality, we used
%$$ (\sqrt{n_1}-\sqrt{p})^4 \cdot (1-p^{-c_\varphi}) \preceq \left((X^{(1)})^\top X^{(1)} \right)^2 \preceq (\sqrt{n_1}+\sqrt{p})^4 \cdot (1+ p^{-c_\varphi}) \quad \text{with high probability},$$
%by Fact \ref{fact_minv} (ii), and the fact that for the product of two PSD matrices, its trace is always nonnegative.
Using the bias limit \eqref{lem_cov_derv_eq} with $\Sigma^{(1)}=\Sigma^{(2)}=\Lambda=V=\id_{p\times p}$, and $w = e_i$ (the $i$-th coordinate vector), we have w.h.p. (via a union bound)
\begin{align*}%\label{eq_bias112}
 e_i^{\top}\hat\Sigma^{-2} e_i = \frac{1}{(n_1+n_2)^2} \left[\frac{a_3+a_4+1}{(a_1+a_2)^2} +\OO(p^{-c_\varphi})\right], \text{ for all } i = 1, 2, \dots, p.
We solve the self-consistent equations \eqref{eq_a34extra} given $a_1, a_2$, and obtain
		a_3 = \frac{p\cdot n_1}{(n_1 +n_2)(n_1 +n_2 - p)}, \quad
		&  a_4 = \frac{p\cdot n_2}{(n_1 + n_2)(n_1 + n_2 - p)}. %\label{simplesovlea34}
Applying $a_3, a_4$ to the equation above, we obtain
\begin{align*}%\label{eq_bias113}
 e_i^{\top}\hat\Sigma^{-2}e_i =  \frac{1}{(n_1+n_2)^2} \left[  \frac{ (n_1+n_2)^3 }{(n_1+n_2-p)^3} +\OO(p^{-c_\varphi})\right], \text{ for all } i = 1, 2, \dots, p.
%In fact, we need this estimate to hold simultaneously for all $1\le i \le p$ with high probability. For this purpose, we shall use equation \eqref{apply derivlocal} to get that
%\begin{align*}%\label{eq_bias113}
%\left| \left(\hat\Sigma^{-2}\right)_{ii} - \frac{1}{(n_1+n_2)^2}\cdot \frac{(n_1+n_2)^3}{(n_1+n_2-p)^3}\right|\prec \frac{p^{-\frac{\varphi-4}{2\varphi}}}{(n_1+n_2)^2}
%\end{align*}
%on a high probability event that does not depend on $i$. Then using Fact \ref{lem_stodomin} (i), we obtain that
%\begin{align*}
%\left| \sum_{i=1}^p \left(\hat\Sigma^{-2}\right)_{ii} - \frac{p}{(n_1+n_2)^2}\cdot  \frac{(n_1+n_2)^3}{(n_1+n_2-p)^3}\right|\prec \frac{p^{1-\frac{\varphi-4}{2\varphi}}}{(n_1+n_2)^2}
%\end{align*}
%with high probability, which by Definition \ref{stoch_domination} gives that
%\begin{align}\label{eq_bias113}
%\left| p^{-1}\sum_{i=1}^p \left(\hat\Sigma^{-2}\right)_{ii} - \frac{1}{(n_1+n_2)^2}\cdot  \frac{(n_1+n_2)^3}{(n_1+n_2-p)^3}\right|\le \frac{p^{-c_\varphi}}{(n_1+n_2)^2}
%\end{align}
%with high probability.
Applying the above result to equation \eqref{eq_bias111}, we get the desired result for the bias term.
%\begin{align*}
%		& \frac{(\sqrt{n_1}-\sqrt{p})^4 \cdot (1- p^{-c_\varphi}) - n_1^2 \cdot (1+\OO(p^{-c_\varphi}))}{(n_1+n_2)^2}\cdot   \frac{(n_1+n_2)^3}{(n_1+n_2-p)^3}\nonumber \\
%		\le &  {p}^{-1}\tr\left[\hat\Sigma^{-2} \left((X^{(1)})^\top X^{(1)} \right)^2\right] - \frac{n_1^2}{(n_1+n_2)^2}\cdot  \frac{(n_1+n_2)^3}{(n_1+n_2-p)^3} \nonumber\\
%		\le &  \frac{(\sqrt{n_1}+\sqrt{p})^4 \cdot (1+ p^{-c_\varphi}) - n_1^2 \cdot (1+\OO(p^{-c_\varphi}))}{(n_1+n_2)^2}\cdot   \frac{(n_1+n_2)^3}{(n_1+n_2-p)^3}.
%\end{align*}
Combining the bias and variance estimates, we get that
	& \left|L(\hat{\beta}_2^{\MTL})  -  \frac{2d^2 n_1^2 (n_1+n_2)}{(n_1 + n_2 - p)^3} - \frac{\sigma^2 p}{n_1+n_2-p}   \right| \\
	  \le &  \left[\left( 1+\sqrt{\frac{p}{n_1}}\right)^4-1\right] \cdot \frac{2d^2n_1^2 (n_1+n_2)}{(n_1 + n_2 - p)^3} \\
	&+\OO\left( p^{-c_\varphi} (\sigma^2 + d^2)+ \frac{d^4 + \sigma^2 d^2}{\kappa^2}+p^{-1/2+2c}\kappa^2 +  p^{-1/4+c} (\sigma^2 +d^2) \right).
Since $\sigma^2 \lesssim  \kappa^2$ and $d^2 \le p^{-\e}{\kappa^2}$ by our assumption, we obtain the desired result.
The proof is complete.
\end{proof}
